\documentclass{article}
\usepackage{enumerate}
\usepackage{verbatim}
\usepackage[parfill]{parskip}
\usepackage[margin = 2.5cm]{geometry}

\usepackage[T1]{fontenc}


\begin{document}

\title{ Ethics Discussion Questions \\ IN618 Security}



1. In a recent American criminal investigation, the FBI has sought Apple's assistance in defeating security features of the iPhone in order to retrieve evidence from one that belonged to a subject of the investigation. Apple has not cooperated and has gone to court to resist the FBI's attempts to compel their cooperation. Is Apple's position ethically sound? Why or why not?

\vspace{10mm}

2. Suppose that a journalist is conducting an investigation of a clearly racist hate group. This journalist asks you to break into an online forum to gather information about the group's members and activities. Would it be ethical to assist the journalist?

\vspace{10mm}

3. Suppose that you know a bank operates a web site that has a serious security vulnerability. An exploit of this vulnerability has the potential to harm its customers. Although the bank has been aware of this problem for six months, there is no indication that the bank is attempting to fix it. What is your ethical responsibility in this situation? What are some difficulties that arise from taking this position?

\vspace{10mm}

4. Suppose that your boss tells you that several employees at your company will be made redundant soon. You are directed to prepare appropriate security measure so that they will not be able to sabotage the company's IT systems or take valuable information from them after they are notified. Of course, you are also told not to tell these people about their upcoming redundancies. But some of the people affected are your friends. Do you tell them? Suppose that you think that one of your friends may do something rash if you tell him. How does this influence your decision?

\vspace{10mm}

5. Suppose that an employer makes IoT gadgets for home use. In a soon-to-be-released device, it chose to do without certain security measures in order to cut costs. In your judgement, the missing security features places customers' privacy at very high risk. You have made your views on this topic known to your employer, but the project will go forward without missing features. What is your ethical responsibility in this case?


\end{document}
